---
title: "W241 Final Project Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data = fread("../data/scored.csv")
```

Tests - T test, difference in means, maybe a regression analysis 

```{r}
data <- data[Diff_found<=15]
```


```{r}
data[,"Score"] = data[,"Pattern_score"] + data[,"RC_score"]+data[,"Diff_score"]+data[,"M_score"]
```

#Model Creation
```{r}
light_mode = data[group=="light_mode"]
dark_mode = data[group=="dark_mode"]
low_contrast = data[group=="low_contrast"]
neon_mode = data[group=="neon"]

```


```{r}
model1 = lm(Score ~ +(group=="dark_mode")+(group=="low_contrast")+(group=="neon"),data=data)
summary(model1)
```
```{r}
robust_CI_1<- coefci(
  x = model1, 
  level = 0.95, 
  vcov. = vcovHC(model1)
  ) 
robust_CI_1
```


```{r}
model2 = lm(Score ~ +(group=="dark_mode")+(group=="low_contrast")+(group=="neon")+as.factor(student_status),data=data)
summary(model2)

```

```{r}
robust_CI_2<- coefci(
  x = model2, 
  level = 0.95, 
  vcov. = vcovHC(model2)
  ) 
robust_CI_2
```
> It seems that there's not a significant effect. However our intuition is correct as the sign of the coefficients for most of our groups is correct. 

# T test for Score
```{r}
light_mode[,Score]
```

Let's perform T tests for each of the questions 
```{r}
t.test(light_mode[,Score],dark_mode[,Score])
```
```{r}
t.test(light_mode[,Score],low_contrast[,Score])
```
```{r}
t.test(light_mode[,Score],neon_mode[,Score])
```


# T test for Reading Comprehension

```{r}
t.test(light_mode[,RC_score],dark_mode[,RC_score])
```
```{r}
t.test(light_mode[,RC_score],low_contrast[,RC_score])
```
```{r}
t.test(light_mode[,RC_score],neon_mode[,RC_score])
```
# T test for Find the Difference 
```{r}
t.test(light_mode[,Diff_score],dark_mode[,Diff_score])
```
```{r}
t.test(light_mode[,Diff_score],low_contrast[,Diff_score])
```
```{r}
t.test(light_mode[,Diff_score],neon_mode[,Diff_score])
```
# T test for Matrix Memorization

```{r}
t.test(light_mode[,M_score],dark_mode[,M_score])
```
```{r}
t.test(light_mode[,M_score],low_contrast[,M_score])
```
```{r}
t.test(light_mode[,M_score],neon_mode[,M_score])
```
# T test for Pattern Matching

```{r}
t.test(light_mode[,Pattern_score],dark_mode[,Pattern_score])
```
```{r}
t.test(light_mode[,Pattern_score],low_contrast[,Pattern_score])
```
```{r}
t.test(light_mode[,Pattern_score],neon_mode[,Pattern_score])
```
```{r}
t.test(light_mode[,Liar_score],dark_mode[,Liar_score])
```
```{r}
t.test(light_mode[,Liar_score],low_contrast[,Liar_score])
```
```{r}
t.test(light_mode[,Liar_score],neon_mode[,Liar_score])
```
# T test for Big Liars

```{r}
t.test(light_mode[,Big_liar_score],dark_mode[,Big_liar_score])
```
```{r}
t.test(light_mode[,Big_liar_score],low_contrast[,Big_liar_score])
```
```{r}
t.test(light_mode[,Big_liar_score],neon_mode[,Big_liar_score])
```










